### 2014-10-22 paper_skeleton.tex
ive added code for tracking mutual information over time and changed figures a bit

\tableofcontents

\section{Abstract}
Learning usually occurs in noisy environments.  In order to make a decision, one must accumulate the  evidence for different alternatives and choose one only once the uncertainty about the choice is sufficiently reduced.  There are two biological systems in which the variables used to make a decision can be described by a random walk: the firing rates of neural populations in the brain of an individual making a decision about a visual stimulus and the beliefs of monkeys about their relative dominance based on the fights they have engaged in.  The same stochastic differential equations can be used to model these quite different systems, which suggests that there are universal principles underlying learning through noisy dynamical systems.  In the neural system, the differential equations are often reduced to a one-dimensional model, but the social system is inherently two-dimensional.  The thresholds dictating when a decision has been made affect both the accuracy of the decision and the expected time until a decision is reached. We find that the dimensionality of the decision process does not affect its accuracy.  We find that if a pair of individuals optimize their thresholds to avoid waiting, a pair making an easy decision will take more time than a pair making a difficult decision.  In a group of individuals optimizing their thresholds to avoid waiting, those pairs making the difficult decisions about high value inputs will have to wait the longest.  Finally, the skewness of the power distribution in the social system is maximized at intermediate waiting costs and the information content of the power distribution is higher when the individual maximize their probability of becoming dominant rather than the accuracy of their decisions. In comparing the output of the model of the social system to data, we found that ...

@@

\subsection{Social }
In groups of pigtailed macaques, different animals have different fighting abilities, and when a pair of animals engages in a fight, one animal may be more likely on average to ``win" the fight.  Over time, as one animal learns that it is likely to lose fights, it will decide to emit a formal subordination signal, communicating its agreeing to the subordinate role in their relationship \citep{Flack:2007kx, Flack:2006fk,Flack:2004oq, Waal:1985fk,Caldecott:1986uk}.  The outcome of a fight is affected by each animal's allies, the presence of those allies, motivation levels,  external environmental variables, and other factors.  Additionally, the number of fights that occur in any period of time depends on similarly stochastic factors.  Because of this stochasticity, the number of fights won and lost in any period of time is a random variable.  Each animal's opinion about its relative dominance, therefore, will perform a biased random walk until one animal's opinion of itself is low enough to agree to being subordinate.

Similar models have previously been applied to animal conflicts, although in that case the model assumed that the animals had perfect memory of their past interactions \citep{Froment:2010fk}

\subsection{Extent and Limits of Analogy }

In Table \ref{variables}, we list the inputs, decision variables, and outputs of the two systems.

%In the neural system, an individual wants to make both a decision that is both quick and accurate.  This is also true in the social system.  However, it may also be the case that a monkey wants to avoid emitting a subordination signal and wants to receive a signal, regardless of whether or not this is the ``correct" outcome, i.e. whether or not he is actually more likely to win a fight.  The criterion used to optimize the threshold, therefore, may be quite different in the two systems.  Additionally, the speed and outcome of the decision process depend on both individuals' thresholds.  Since an individuals' best behavior depends on the behavior of the other animal, optimizing the threshold has a strategic aspect.

@@

%note about applicability to quorum sensing?!?

@@

If enough events happen in the period of time from $t$ to $t+\tau$ then we can approximate the Poisson random variables with Normal random variables with mean and variance equal to the mean of the Poisson random variables.  Our second assumption, then, is that the period of time of length $\tau$ is long enough to make this approximation. Let $Z_\text{L}$ and $Z_\text{R}$, be independent standard Normal random variables, i.e. with mean $0$ and standard deviation $1$.  Then our equations for $X_i(t+\tau)$ become
\begin{align*}
X_1(t+\tau)&=(1-\ell\tau)X_1(t)+b\bigg(\tau rc+\sqrt{\tau rc}Z_{\text{L}}\bigg)-b\bigg(\tau r(1-c)+\sqrt{\tau r(1-c)}Z_{\text{R}}\bigg)
\\X_2(t+\tau)&=(1-\ell\tau)X_2(t)-b\bigg(\tau rc+\sqrt{\tau rc}Z_{\text{L}}\bigg)+b\bigg(\tau r(1-c)+\sqrt{\tau r(1-c)}Z_{\text{R}}\bigg).
\end{align*}
Finally, as we make the period of time shorter and shorter, making $\tau$ infinitesimally small, these equations become stochastic differential equations,
\begin{equation}
\begin{array}{ll}
dX_1&=\bigg(-\ell X_1(t)+br(2c-1)\bigg)dt+\bigg(b\sqrt{rc}\bigg)dW_\text{L}t-\bigg(b\sqrt{r(1-c)}\bigg)dW_\text{R}t
\\dX_2&=\bigg(-\ell X_2(t)-br(2c-1)\bigg)dt-\bigg(b\sqrt{rc}\bigg)dW_\text{L}t+\bigg(b\sqrt{r(1-c)}\bigg)dW_\text{R}t
\end{array}
\end{equation}
where $dW_{\text{L}}$ and $dW_{\text{R}}$ are independent Brownian motions representing, respectively, the left and right inputs.  The assumptions about the timescales on which inputs occur are particularly reasonable in the social system, although the successful application of this type of model to neural populations implies they are not unreasonable in that system.

%\begin{equation}
%\begin{array}{ll}
%dX_1&=\bigg(-\ell X_1(t)+b(2d-1)\bigg)dt+b\sqrt{d}dW_{1}t-b\sqrt{(1-d)}dW_{2}t
%\\dX_2&=\bigg(-\ell X_1(t)+b(1-2d)\bigg)dt-b\sqrt{d}dW_{1}t+b\sqrt{(1-d)}dW_{2}t,
%\end{array}
%\end{equation}
\subsection{Reaching a decision }
Each decision variable, $X_1$ and $X_2$, accumulates information about the stimulus.  The sign and size of the two variables indicate how much evidence there is for each possible decision outcome.  When a lot of evidence for the first possibility has been observed, $X_1$ will be large and positive, and similarly for the second possibility.  If the difference in the variables can be observed, the difference indicates the relative strengths of the evidence for either possibility. If $Y=X_1-X_2$, when $Y$ is large enough the system decides on $X_1$ and when $Y$ is low enough the system decides on $X_2$.  Specifically, there are two thresholds, $T_2$ and $T_1$ such that if $Y>T_1$ the decision is for $X_1$ and if $Y<-T_2$ the decision is for $X_2$.  However, it may be the case that the difference in the variables cannot be observed.  In this case, the decision depends on whether $X_1$ or $X_2$ hits a threshold first.  Again, there are two thresholds, $T_2$ and $T_1$, and if $X_1<-T_1$ the decision is for $X_1$ and if the $X_2<-T_2$ the decision is for $X_2$.

In the neural system, the two stochastic equations describing the activity of the two neural populations integrating environmental evidence are often reduced to the one-dimensional equation describing the difference in the activity levels to make the system easier to analyze \cite{Brown:2005fk,Bogacz:2006uq,Feng:2009kl}.  However, in the social system we are considering, we cannot make any assumptions about the existence of a third party evaluating the difference in the opinions of the two animals.  A ``decision," i.e. the emission of a signal from one of the two animals, is only reached when one of the two animals' opinions goes below a certain threshold.  The social system is therefore inherently two-dimensional, whereas the neural system may be adequately described by one dimension.

\subsection{Utility of the decision }
The thresholds affect the expected time until a decision is reached (decision time, DT) and the probability that an incorrect decision is made (error rate, ER).  The thresholds also affect the probability that either variable will ``give up'' first.  In the social case, this is the probability that each animal will emit a subordination signal (signaling probability, $\text{SP}_i$).  In the neural case, ??? These quantities, DT, ER, and $\text{SP}_i$, satisfy partial differential equations with respect to the starting values of the decision variables. In Appendix \ref{pdes_deriv}, we derive these partial differential equations.  While an analytical solution is known in the one-dimensional case, the two-dimensional case is analytically intractable.  We therefore numerically solve the PDEs in the two-dimensional case.  In Table \ref{models}, we compare how the decision is made and how the decision process is optimized in the two systems.

@@

\subsection{Consensus }
Consensus about the value of each individual in a group emerges out of the decision process.  In the social system, an animal's social power depends on the consensus in the group about its fighting ability \cite{Flack:2004oq,Flack:2006uq,Brush:2013fk}.  Given the decisions that each pair of individuals reaches, there are measures of the consensus in the group that successfully predict an animal's social power and also extend to other social systems \cite{Brush:2013fk}.  For each random set of fighting abilities, we let the animals optimize their thresholds, which give the probability that each pair will reach either decision, and we then generate a set of decisions given by these probabilities.  Given this signaling network, we use various formalisms to measure the consensus about each node in the network, i.e. a power score for each animal in the group.  For many random sets of fighting abilities, we can find the mutual information between the power score and the true fighting abilities. This tells us how informative observing the outcomes of the decisions is about the underlying fighting abilities.  We also find the average skewness of the power distributions.

@@

\subsection{Prioritizing signaling probability does not always decrease pairwise decision accuracy. }
We first look at the Nash equilibrium thresholds when the animals only care about one property of the decision (error rate, signaling property, or decision time).  In these extremes, the Nash thresholds do not depend on how difficult the decision is. The pair can make the most accurate decision if the weaker animal chooses a low threshold and the strong animal chooses a high one, so if only error rate matters ($w_1=1$, $w_2=0$, $w_3=0$), those will be the Nash  thresholds.   If only signaling probability matters ($w_1=0$, $w_2=0$, $w_3=1$), there is no incentive for the individuals to stop accumulating evidence (fighting, in the social case) so both individuals wait until the other gives up and the Nash  thresholds are both high.  If only decision time matters ($w_1=0$, $w_2=1$, $w_3=1$), both animals have an incentive to set their thresholds low and reach a decision quickly, whatever that decision may be (Figure \ref{nasheq_thresholds}).   Notice that in changing from prioritizing signaling probability ($w_3=1$) to prioritizing decision time ($w_2=1$), first the weaker animal lowers its threshold and \emph{then} the stronger animal lowers his.

@@

The thresholds affect the accuracy and decision time with which a pair can reach a decision.  For a difficult decision ($c$ close to $.5$), the accuracy with which a pair using Nash thresholds can reach a decision is highest when only error rate matters ($w_1=1$) and lowest when only signaling probability matters ($w_3=1$).  Accuracy decreases as the weight given to decision time increases (Figure \ref{nasheq_thresholds}).  Since, for sufficiently high waiting costs, the Nash thresholds do not depend on the tradeoff between error rate and signaling probability, neither does the accuracy for a pair using Nash thresholds.  In other words, once waiting costs are high, a pair of animals each minimizing error rate and a pair minimizing signaling probability will reach a decision with the same accuracy.

\subsection{Intermediately difficult decisions sometimes take the longest. }

@@

\subsection{Decisions in a group context take longest between animals with similarly high abilities. }

After analyzing Nash equilibrium thresholds between pairs of animals, we found the optimal thresholds for a group of animals ($N=20$) such that no animal had an incentive to choose a different threshold.  As with pairwise Nash thresholds, when the animals only care about signaling probability ($w_3=1$), all animals in the group choose high thresholds, whereas if they only care about decision time ($w_2=1$), all animals choose low thresholds.  When the animals only care about accuracy ($w_1=1$), all animals choose high thresholds, except the weakest who choose a low threshold.  At intermediate weights, thresholds decrease as position in the group decreases (Figure \ref{groupeq_thresholds}).

When waiting costs are low, the pairs that take the longest to reach a decision are those with similar fighting abilities, but pairs with less similar abilities also take a fairly long time.  When waiting costs are high, most pairs can reach a decision quite quickly, except those who have similar and high abilities (Figure \ref{groupeq_thresholds}).  The average accuracy decreases as waiting costs increase (Figure \ref{groupeq_thresholds}).

As soon as any waiting costs are introduced, as with the pairwise Nash thresholds, the weaker animals have incentives to lower their thresholds to make quicker decisions at the expense of accuracy.  This incentive is stronger when error rate is more important than signaling probability.  The result is that all the weakest animals set their thresholds as low as possible, making the accuracy of decisions between those animals very poor and decreasing the overall accuracy of the group. In other words, average accuracy \emph{increases} as signaling probability is prioritized over error rate, except when there are no waiting costs (Figure \ref{groupeq_thresholds}). The mutual information of any measure of consensus in the signaling network increases (more or less) with accuracy so it too increases as signaling probability becomes more important.

@@

\section{Discussion}
what's interesting and exciting and new?

we can derive sde's from first principles

prioritizing signaling probability sometimes makes decision more accurate

prioritizing waiting costs change which decisions take the longest

optimization weights change the overall social structure

extension of neural model by removing third party comparison and allow individuals to minimize signaling probability

extension of game theory by introducing heterogeneous abilities

extension of David's paper

explanation for variation across species of macaque

evolutionary implications

%comparison to social data
Empirically, those pairs of monkeys that take the longest to establish a signaling dynamics are those with the most similar fighting abilities...

skewness
they're using eigenvector centrality

\begin{figure}[ht]
\includegraphics[width=\textwidth]{/Users/eleanorbrush/Desktop/pairwise_accuracy.pdf}
\includegraphics[width=\textwidth]{/Users/eleanorbrush/Desktop/nasheq_thresholds.pdf}
\caption{\label{nasheq_thresholds}  The accuracy of a pair using Nash equilibrium thresholds decreases as the weight given to decision time increases.  (a) In the upper panel, the color indicates the accuracy of a decision made by a pair making a difficult decision ($c=.55$) using Nash equilibrium thresholds, as a function of the optimization weights, $w_1$, $w_2$, $w_3$.  In the lower left corner of the simplex, only error rate matters ($w_1=1$).  In the upper corner, only decision time matters ($w_2=1$).  In the lower right corner, only signaling probability matters ($w_3=1$). Accuracy decreases as $w_2$ increases but is not greatly affected by a tradeoff between $w_1$ and $w_3$. In (b)-(g) we show how the Nash equilibrium thresholds (top row) and decision time for a pair using those thresholds (bottom row) depends on the difficulty of the decision ($c$). The optimization weights for each panel are indicated in the simplex with the corresponding letter.  At intermediate waiting costs (f), intermediately difficult decision take the longest.}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{/Users/eleanorbrush/Desktop/groupaccuracy_heatmap.pdf}
\includegraphics[width=\textwidth]{/Users/eleanorbrush/Desktop/groupeq_thresholds.pdf}
\caption{\label{groupeq_thresholds}   The accuracy of a group using optimal thresholds decreases as the weight given to decision time increases.  In the upper panels, the color indicates the average accuracy of the decisions between individuals in the bottom quartile (a) and the average accuracy of the whole group (b) using optimal thresholds, as a function of the optimization weights, $w_1$, $w_2$, $w_3$.  In the lower left corner of the simplex, only error rate matters ($w_1=1$).  In the upper corner, only decision time matters ($w_2=1$).  In the lower right corner, only signaling probability matters ($w_3=1$). Both bottom-quartile and total accuracy decrease as $w_2$ increases, and the increase in bottom-quartile accuracy as $w_3$ increases drives a slight increase in total accuracy.  In (c)-(h) we show how the group-context optimal thresholds (top row) and decision time for each pair (bottom row) depends on the true order of ability where $1$ is the strongest animal and $20$ is the weakest. The optimization weights for each panel are indicated in the simplex with the corresponding letter.  For low waiting costs (c and d), it takes longest for pairs with similar ability to reach a decision.  For slightly higher waiting costs (f and g), it takes longer for pairs with similar and high ability to reach a decision.}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=\textwidth]{/Users/eleanorbrush/Desktop/skewness_heatmap.pdf}
\caption{\label{skewness} The skewness of the distribution of the number of signalers is maximized at intermediate waiting costs. In the lower left corner of the simplex, only error rate matters ($w_1=1$).  In the upper corner, only decision time matters ($w_2=1$).  In the lower right corner, only signaling probability matters ($w_3=1$).}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=\textwidth]{/Users/eleanorbrush/Desktop/mostinformative_heatmap.pdf}
\caption{\label{bestmetric}  Which measure of consensus is most informative about fighting ability depends on how accurate decision are on average.  When decision are very accurate or very inaccurate, measures of the number of signals received are most informative.  When accuracy is slightly lower, eigenvector centrality of the signaling network is most informative.  When accuracy is slightly lower again, the number of signalers is most informative.  When accuracy is lower still, the entropy of signals received is most informative.  In the lower left corner of the simplex, only error rate matters ($w_1=1$).  In the upper corner, only decision time matters ($w_2=1$).  In the lower right corner, only signaling probability matters ($w_3=1$).}
\end{figure}

\begin{table}[ht]
\centering
\caption{\label{variables}{\bf  Variables and interpretations in neural and social systems.} }
\ra{1.3}
\begin{tabular}{@{}rllll@{}}
Variable & Interpretation & Neural &   Social \\
\cmidrule{1-4} 
& input & dots moving left or right & fights won or lost
\\$c$ & strength of input & coherence of dots & probability of stronger animal winning
\\$X_1,X_2$ & decision variables &  firing rates of neural populations & opinions about relative dominance
\\ & dist. of states of the world & left / right equally likely & distribution of fighting abilities
\\ & decision & subject indicates left or right & one animal emits a subordination signal
\\ & correct decision & subject chooses correct direction & weaker animal signals
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{\label{models}{\bf  Comparison of models applied to neural and social systems.} Differences are highlighted in red.}
\ra{1.3}
\begin{tabular}{@{}rllll@{}}
& \multicolumn{2}{c}{Neural} &  Social \\
\cmidrule{2-3} \cmidrule{4-4} 
%model  & DDM or OU & race && race with leak
%\\
dimensionality & $1$  && $2$
\\decision & difference hits a threshold  && \fcolorbox{red}{white}{one var. hits a threshold}
\\ optimality criterion &  reward from being ``right" && reward from being ``right"
\\ & decision time && decision time
\\ & && \fcolorbox{red}{white}{reward from  receiving signal}
\\optimization depends on & input strength && input strength
\\ & noise && noise
\\ & leak rate && leak rate
\\ & && \fcolorbox{red}{white}{other animal's threshold}
\end{tabular}
\end{table}

>>>>

%\tableofcontents

\section{Abstract}
%Learning usually occurs in noisy environments.  In order to make a decision, one must accumulate the  evidence for different alternatives and choose one only once the uncertainty about the choice is sufficiently reduced.  There are two biological systems in which the variables used to make a decision can be described by a random walk: the firing rates of neural populations in the brain of an individual making a decision about a visual stimulus and the beliefs of monkeys about their relative dominance based on the fights they have engaged in.  The same stochastic differential equations can be used to model these quite different systems, which suggests that there are universal principles underlying learning through noisy dynamical systems.  In the neural system, the differential equations are often reduced to a one-dimensional model, but the social system is inherently two-dimensional.  The thresholds dictating when a decision has been made affect both the accuracy of the decision and the expected time until a decision is reached. We find that the dimensionality of the decision process does not affect its accuracy.  We find that if a pair of individuals optimize their thresholds to avoid waiting, a pair making an easy decision will take more time than a pair making a difficult decision.  In a group of individuals optimizing their thresholds to avoid waiting, those pairs making the difficult decisions about high value inputs will have to wait the longest.  Finally, the skewness of the power distribution in the social system is maximized at intermediate waiting costs and the information content of the power distribution is higher when the individual maximize their probability of becoming dominant rather than the accuracy of their decisions. In comparing the output of the model of the social system to data, we found that ...

@@

\subsection{Social }
In groups of pigtailed macaques, different animals have different fighting abilities, and when a pair of animals engages in a fight, one animal may be more likely on average to ``win" the fight.  Over time, as one animal learns that it is likely to lose fights, it will decide to emit a formal subordination signal, communicating its agreeing to the subordinate role in their relationship \citep{Flack:2007kx, Flack:2006fk,Flack:2004oq, Waal:1985fk,Caldecott:1986uk}.  The outcome of a fight is affected by each animal's allies, the presence of those allies, motivation levels,  external environmental variables, and other factors.  Additionally, the number of fights that occur in any period of time depends on similarly stochastic factors.  Because of this stochasticity, the number of fights won and lost in any period of time is a random variable.  Each animal's opinion about its relative dominance, therefore, will perform a biased random walk until one animal's opinion of itself is low enough to agree to being subordinate.  A similar model has previously been applied to animal conflicts, although in that case the model assumed that the animals had perfect memory of their past interactions \citep{Froment:2010fk}.

@@

%note about applicability to quorum sensing

@@

If enough events happen in the period of time from $t$ to $t+\tau$ then we can approximate the Poisson random variables with Normal random variables with mean and variance equal to the mean of the Poisson random variables.  Our second assumption, then, is that the period of time of length $\tau$ is long enough to make this approximation. Let $Z_\text{L}$ and $Z_\text{R}$, be independent standard Normal random variables, i.e. with mean $0$ and standard deviation $1$.  Then our equations for $X_i(t+\tau)$ become
\begin{align*}
X_1(t+\tau)&=(1-\ell\tau)X_1(t)+b\bigg(\tau rc+\sqrt{\tau rc}Z_{\text{L}}\bigg)-b\bigg(\tau r(1-c)+\sqrt{\tau r(1-c)}Z_{\text{R}}\bigg)
\\X_2(t+\tau)&=(1-\ell\tau)X_2(t)-b\bigg(\tau rc+\sqrt{\tau rc}Z_{\text{L}}\bigg)+b\bigg(\tau r(1-c)+\sqrt{\tau r(1-c)}Z_{\text{R}}\bigg).
\end{align*}
Finally, as we make the period of time shorter and shorter, making $\tau$ infinitesimally small, these equations become stochastic differential equations,
\begin{equation}
\begin{array}{ll}
dX_1&=\bigg(-\ell X_1(t)+br(2c-1)\bigg)dt+\bigg(b\sqrt{rc}\bigg)dW_\text{L}t-\bigg(b\sqrt{r(1-c)}\bigg)dW_\text{R}t
\\dX_2&=\bigg(-\ell X_2(t)-br(2c-1)\bigg)dt-\bigg(b\sqrt{rc}\bigg)dW_\text{L}t+\bigg(b\sqrt{r(1-c)}\bigg)dW_\text{R}t
\end{array}
\end{equation}
where $dW_{\text{L}}$ and $dW_{\text{R}}$ are independent Brownian motions representing, respectively, the left and right inputs.  The assumptions about the timescales on which inputs occur are particularly reasonable in the social system, although the successful application of this type of model to neural populations implies they are not unreasonable in that system.  In Table \ref{variables}, we list the inputs, outputs, and variables of the decision model and how they should be interpreted in the neural and social systems.

\subsection{Reaching a decision }
Each decision variable, $X_1$ and $X_2$, accumulates information about the stimulus.  The sign and size of the two variables indicate how much evidence there is for each possible decision outcome.  When a lot of evidence for the first possibility has been observed, $X_1$ will be large and positive, and similarly for the second possibility.  If the difference in the variables can be observed, the difference indicates the relative strengths of the evidence for either possibility. If $Y=X_1-X_2$, when $Y$ is large enough the system decides on $X_1$ and when $Y$ is low enough the system decides on $X_2$.  Specifically, there are two thresholds, $T_2$ and $T_1$ such that if $Y>T_1$ the decision is for $X_1$ and if $Y<-T_2$ the decision is for $X_2$.  However, it may be the case that the difference in the variables cannot be observed.  In this case, the decision depends on whether $X_1$ or $X_2$ hits a threshold first.  Again, there are two thresholds, $T_2$ and $T_1$, and if $X_1<-T_1$ the decision is for $X_1$ and if the $X_2<-T_2$ the decision is for $X_2$.

In the neural system, the two stochastic equations describing the activity of the two neural populations integrating environmental evidence are often reduced to the one-dimensional equation describing the difference in the activity levels to make the system easier to analyze \cite{Brown:2005fk,Bogacz:2006uq,Feng:2009kl}.  However, in the social system we are considering, we cannot make any assumptions about the existence of a third party evaluating the difference in the opinions of the two animals.  A ``decision," i.e. the emission of a signal from one of the two animals, is only reached when one of the two animals' opinions goes below a certain threshold.  The social system is therefore inherently two-dimensional, whereas the neural system may be adequately described by one dimension.  In Table \ref{differences}, we compare how the decision is made and how the decision process is optimized in the two systems.

\subsection{Utility of the decision }
The thresholds affect the expected time until a decision is reached (decision time, DT) and the probability that an incorrect decision is made (error rate, ER).  The thresholds also affect the probability that either variable will ``give up'' first.  In the social case, this is the probability that each animal will emit a subordination signal (signaling probability, $\text{SP}_i$).  In the neural case, ??? These quantities, DT, ER, and $\text{SP}_i$, satisfy partial differential equations with respect to the starting values of the decision variables. In Appendix \ref{pdes_deriv}, we derive these partial differential equations.  While an analytical solution is known in the one-dimensional case, the two-dimensional case is analytically intractable.  We therefore numerically solve the PDEs in the two-dimensional case.

@@

\subsection{Consensus }
Consensus about the value of each individual in a group emerges out of the decision process.  In the social system, an animal's social power depends on the consensus in the group about its fighting ability \cite{Brush:2013fk,Flack:2004oq,Flack:2006uq}.  Given the decisions that each pair of individuals reaches, there are measures of the consensus in the group that successfully predict an animal's social power and also extend to other social systems \cite{Brush:2013fk}.  For each random set of fighting abilities, we let the animals optimize their thresholds, which give the probability that each pair will reach either decision, and we then generate a set of decisions given by these probabilities.  Given this signaling network, we use various formalisms to measure the consensus about each node in the network, i.e. a power score for each animal in the group.  For many random sets of fighting abilities, we can find the mutual information between the power score and the true fighting abilities. This tells us how informative observing the outcomes of the decisions is about the underlying fighting abilities.  We also find the average skewness of the power distributions.

@@

\subsection{Prioritizing signaling probability does not always decrease pairwise decision accuracy. Intermediately difficult decisions sometimes take the longest. }
We first look at the Nash equilibrium thresholds when the animals only care about one property of the decision (error rate, signaling property, or decision time).  In these extremes, the Nash thresholds do not depend on how difficult the decision is. The pair can make the most accurate decision if the weaker animal chooses a low threshold and the strong animal chooses a high one, so if only error rate matters ($w_1=1$, $w_2=0$, $w_3=0$), those will be the Nash  thresholds.   If only signaling probability matters ($w_1=0$, $w_2=0$, $w_3=1$), there is no incentive for the individuals to stop accumulating evidence (fighting, in the social case) so both individuals wait until the other gives up and the Nash  thresholds are both high.  If only decision time matters ($w_1=0$, $w_2=1$, $w_3=1$), both animals have an incentive to set their thresholds low and reach a decision quickly, whatever that decision may be (Figure \ref{nasheq_thresholds}).   Notice that in changing from prioritizing signaling probability ($w_3=1$) to prioritizing decision time ($w_2=1$), first the weaker animal lowers its threshold and \emph{then} the stronger animal lowers his.

@@

The thresholds affect the accuracy and decision time with which a pair can reach a decision.  For a difficult decision ($c$ close to $.5$), the accuracy with which a pair using Nash thresholds can reach a decision is highest when only error rate matters ($w_1=1$) and lowest when only decision time matters ($w_2=1$).  When waiting costs are low, accuracy decreases as the weight given to signaling probability increases (Figure \ref{nasheq_thresholds}).  For sufficiently high waiting costs, the Nash thresholds do not depend on the tradeoff between error rate and signaling probability, so neither does the accuracy for a pair using Nash thresholds.  In other words, once waiting costs are high, a pair of animals minimizing error rate and a pair each of whom minimizes his signaling probability will reach a decision with the same accuracy.

@@

\subsection{Average group accuracy increases as signaling probability becomes more important. Decisions in a group context take longest between animals with similarly high abilities. }

To study decision making in a group, we find the optimal thresholds for a group of animals ($N=20$) such that no animal had an incentive to choose a different threshold.  As with pairwise Nash thresholds, when the animals only care about signaling probability ($w_3=1$), all animals in the group choose high thresholds, whereas if they only care about decision time ($w_2=1$), all animals choose low thresholds.  When the animals only care about accuracy ($w_1=1$), all animals choose high thresholds, except the weakest who choose a low threshold.  At intermediate weights, thresholds decrease as position in the group decreases (Figure \ref{groupeq_thresholds}).

The average accuracy decreases as waiting costs increase (Figure \ref{groupeq_thresholds}).  As soon as any waiting costs are introduced, as with the pairwise Nash thresholds, the weaker animals have incentives to lower their thresholds to make quicker decisions at the expense of accuracy.  This incentive is stronger when error rate is more important than signaling probability.  The result is that all the weakest animals set their thresholds as low as possible, making the accuracy of decisions between those animals very poor and decreasing the overall accuracy of the group. In other words, average accuracy \emph{increases} as signaling probability is prioritized over error rate, except when there are no waiting costs (Figure \ref{groupeq_thresholds}). The mutual information of any measure of consensus in the signaling network increases (more or less) with accuracy so it too increases as signaling probability becomes more important.  
%% hit harder that different parts of the group are making the tradeoff differently and that accuracy really does increase!!  that's a difference between pairs and groups!!!  and hit harder in the discussion too.

When waiting costs are low, the pairs that take the longest to reach a decision are those with similar fighting abilities, but pairs with less similar abilities also take a fairly long time.  When waiting costs are high, all pairs reach decision quickly.  At intermediate costs, most pairs can reach a decision quite quickly, except those who have similar and high abilities (Figure \ref{groupeq_thresholds}).

@@

\section{Discussion}

Starting with a simple and reasonable description of how fights occur between pairs of animals in a social group and how the outcomes of those fights affect the animals' opinions of their relative dominance, we derived  a model in which those opinions change according to stochastic differential equations.  A nearly identical model has previously been used to describe decision making in primate brains where the decision is determined by the firing rates of two neural populations.  The model reduces to previously studied ``war of attrition'' games in the game theory literature when the abilities of the two animals are the same.  Conflict and strategy are not usually ascribed to the neural model and the war of attrition is not usually thought of as a process through which the pair of competitors reaches a decision about an external environment.  The similarities between these three frameworks-- social decision making, neural decision making, and a game-- suggest that there are common principles of decision making through conflict that are applicable to a number of systems.

In the kind of leaky integrator models we studied here, either the absolute value of the decision variables or the difference in their values can determine the outcome of the decision.  We find that, for a given decision time, the accuracy of the decision does not depend on which of these mechanisms is used.  In order for the difference in variables to be used, a third party arbiter needs to be present to evaluate the value of each decision variable and find their difference.  In the brain, it might be the case that there is a third neural population whose activity depends on the two populations gathering input, but in a social group, there is not a third party informing how a pair of animals should establish their subordination-dominance relationship.  The fact, then, that the model does not depend on the existence of this third party arbiter means that it can be equally well applied whether or not it is present.

Any method for making a decision reaches each output with a given probability, reaches the ``correct" output with an error rate, and makes a decision in an expected decision time. If each individual involved in the decision prefers a different output, the pair is in conflict and choosing appropriate strategies has a strategic aspect.  The individuals can make a tradeoff between how valuing their personal preference and valuing the correct output.  We expected to find that individuals valuing their personal preference at the expense of the correct output would tend to make decisions that were less accurate.  However, if decision time is sufficiently important, than the tradeoff between the other two variables does not affect the strategies the pair chooses.  In fact, when there is a group of animals all making this tradeoff, increasing the importance of personal preferences over accuracy improves the accuracy with which animals in the bottom of the group resolve their differences, increasing the average accuracy of the whole group.  It is usually assumed that neural populations in the brain are in agreement about the desired outcome, since the whole organism receives a benefit from making a correct decision in a short time.  But it is not implausible that different neural populations would prefer to make different decisions and we find that introducing this conflict into the model of decision making could actually improve overall accuracy.

In a pair of individuals making a decision, the difference in their abilities, not their absolute values, determines how quickly they can reach a decision.  When waiting costs are high or low, more difficult decisions take longer to make.  However, at intermediate waiting costs we find that it takes the longest to reach decisions of intermediate difficulty.  The waiting costs affect pairs making difficult decisions and pairs making intermediate decisions differently, such that a pair making a difficult decision does better off by ignoring the output of the decision and just reaching the decision quickly.

The costs of decision time, error rate, and signaling probability also affect the decision times of decisions in a group context.  In a group context, each pair of animals experiences the difference in their abilities, but their absolute positions within the group also matter.  In this context, at intermediate waiting costs, the longest decisions are those between pairs who have similar and high abilities.  In data from a captive population of macaques, we observe that pairs of animals with high abilities \emph{do} reach agreements about their relative dominance but that pairs of animals with low abilities sometimes do not reach such agreements.  This indicates that our simple model is missing a level of social complexity that could explain this empirical pattern.

There are (at least) two modifications to the model that we expect would produce results closer to the empirical observations.  First, in the model, the rates at which animals fight each other do not depend on the abilities of the animals.  However, it is likely that animals with lower abilities are less mobile and encounter their peers at a lower rate than animals with higher abilities who are more free to range throughout the group.  In the model, this heterogeneity in encounter rate would make the decisions between animals with low encounter rates take longer.  Second, in the model, all animals value signaling probability, error rate, and waiting costs equally.  However, it is likely that the benefits from receiving a subordination signal from a partner and the costs of fighting depend on the ability on both animals' ability.  If animals with low ability  do not value an agreement with other animals with similar abilities, there would be less incentive for them to reach an agreement.

With the goal of keeping the model simple and interpretable, we did not allow parameters like encounter rates and optimization weights to vary across the group of animals, although they are likely to in the empirical system.  Even with the small number of parameters we did consider, we find systematic variation in group-level properties that are observable in the data.  We find that the skewness of the distribution of power scores, given by a number of measures of power \cite{Brush:2013fk,Flack:2006uq}, is maximized at intermediate waiting costs.  In our data, we observe a right-skewed distribution of power.  To the extent that our model recapitulates the empirical system, this would suggest that waiting costs are neither the only priority nor are they ignored completely.

In a more complicated model, the ``aggressiveness'' of animals moving in a spatially explicit area affected the shape of the dominance hierarchy \cite{Hemelrijk:2011fk}.  While the mechanisms of that model are quite different, ``aggressiveness'' could be argued to be similar to disregarding waiting costs and prioritizing signaling probability.  Neither the authors of that work nor we found that a difference in the underlying distribution of fighting abilities is required to change the distribution of dominance or power.  In other words, in both models, the collective computation that results in a power structure emerges out of how the individuals interact and collect information rather than from the distribution of fighting abilities.

The variation in skewness of the power distribution is interesting because the power structures typical to different species of macaque vary in their average skewness \cite{Flack:2004oq,Preuschoft:2004ly,Waal:1985fk}.  One explanation might be that the distribution of fighting abilities is different from species to species, for instance because there is more or less variation in body size.  However, our model suggests that even if the underlying distribution of fighting abilities are identical, the priorities given to signaling probability, error rate, and waiting costs can affect the distribuiton of power.  The benefit of having a partner agree to be subordinate, the benefit or reaching the ``correct" agreement, and the costs of fighting may vary from species to species, causing variation in the shape of the power structure.

The other feature of the signaling network that changes as a function of the optimization weight is which measure of power is most informative about the underlying fighting abilities.  There are many measures of a network that might seem like reasonable ways to measure the consensus about each individual's ability.  As network scientists, we would like to know when which measure is the most informative and we find that it depends on how accurately a decision between paris reflects the difference in their abilities.  If we expect relatively high but imperfect pairwise accuracy then a global metric like eigenvector centrality is the best.  As members of a social group about which they would like to have information, the monkeys may use these measures (or approximations of them) to estimate their own and their peers' abilities.  In previous work, we used both eigenvector centrality and measures of the number of signals received to measure the consensus about node status in empirical networks and found that both were produced scores that were informative about the nodes' functional behavior.  This suggests... %%%

%extension of game theory by introducing heterogeneous abilities
%
%extension of David's paper
%
%evolutionary implications
%
%they're using eigenvector centrality
